---
title: "Baby Names"
output: html_document
---

<script type="text/javascript" src="../utils/menu.js"></script>

### Loading Data

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

To begin loading the data, we first download the list of US states and their abbreviations from [jasonong on Github](https://github.com/jasonong/List-of-US-States).

```{r setup, results = "hide"}
library(tidyverse)
download.file("https://raw.githubusercontent.com/jasonong/List-of-US-States/master/states.csv",
              "../data/states.csv")
states = read_csv("../data/states.csv")
states
```

Now we define a function to load a tibble containing the name data for a specific state abbreviation, `load_state_data`.

```{r load-data-fun}
load_state_data = function (state) {
  read_csv(
    file.path("..", "data", paste0(state, ".txt")),
    col_names = c("state", "sex", "year", "name", "occurances"),
    col_types = cols(sex = col_character())
  )
}

load_state_data("AL")
```

To quickly load all of the states, we implement `concatenate_tables` below which applies the `load_state_data` to each element in `states$Abbreviation`. It then binds all of the tibbles together using `bind_rows`.

```{r concatenate}
concatenate_tables = function () {
  state_abbrevs = states$Abbreviation
  tables = lapply(state_abbrevs, load_state_data)
  bind_rows(tables)
}

concatenated = concatenate_tables()
concatenated
```

For later use, we export the `concatenated` table as a CSV file.

```{r export}
write_csv(
  concatenated,
  file.path("..", "data", "all-states.csv")
)
```

